Estimación de Mortalidad por departamentos: el caso de la región Pampeana (2009-2011)

### 2020-01-31 analysis/Paper_draft_ESP.Rmd
Visto Nico

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(kableExtra)
# change your dire
Dire="C:/Proyectos/SubnMort/"
load(paste0(Dire,"analysis/Rmarkdown_variables.RData"))
# rmarkdown::render('Paper_draft_ESP.Rmd', encoding="UTF-8")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(kableExtra)
# change your dire
load("analysis/Rmarkdown_variables.RData")
# rmarkdown::render('Paper_draft_ESP.Rmd', encoding="UTF-8")
```
